\documentclass{resume}

\rohead{\thepage\ of \pageref{LastPage}}

\cofoot{
	\begin{spacing}{0.8}
%%	\so{Address, Line 2, City, ST 00000} \\
	\small{
%%		\footerphone{(555) 555-5555} \
		\footerlink{http://jakefolio.com/} \
		\footeremail{jake.smith92@gmail.com}
	} \\
	\small{\emph{
		\LaTeX source for this resum$\acute{e}$ located at \href{https://github.com/jakefolio/resume}{github.com/jakefolio/resume}
	}}
	\end{spacing}
}

\begin{document}

\name{Jake Smith}

\smallskip

\section{Skills}

\stdtable{
Languages  & PHP, Ruby, JavaScript, node.js, SQL, HTML, CSS\\
Tools      & Zend Framework, Symfony, Fuel, Laravel, Doctrine, Rails, Sinatra, jQuery, Git, LESS/SASS\\
Services   & Amazon S3\\
           & \emph{APIs}: Twitter, Foursquare, YouTube\\
DBs        & MySQL, PostgreSQL, MongoDB\\
Systems    & OSX, Red Hat Enterprise Linux 5/6, CentOS\\
}

\section{Experience}

\employer
	{iSight Partners}
	{http://isightpartners.com}
	{July 2012 --- \emph{Present}}
	{Sr. Software Developer}
	{Developed a replacement for a legacy portal system. I worked on many key pieces of the application, including but not limited to: API endpoint creation/integration, frontend development (HTML, CSS, JavaScript), rebuilding Authentication System and Creating Data Sync System.}
\\ \\ \\
\employer
	{Click Here}
	{http://clickhere.com}
	{December 2011 --- July 2012}
	{Interactive Developer}
	{As an Interactive Developer I help mentor junior developers and architect applications.}
\\ \\ \\
\employer
	{RAPP}
	{http://rapp.com}
	{April 2011 --- December 2011}
	{Interactive Software Engineer}
	{Developer for high profile travel website. Built an interactive trivia game using node.js, HTML \& PHP for client prototype. Utilize the Agile methodology to provide an efficient and streamlined process.}
\\ \\ \\
\employer
	{Click Here}
	{http://clickhere.com}
	{January 2010 --- April 2011}
	{Interactive Developer}
	{As an Interactive Developer I help mentor junior developers and architect applications.}
\\ \\ \\
\employer
	{Get Legal}
	{http://getlegal.com/}
	{January 2008 --- January 2010}
	{Sr. Web Application Developer}
	{At getlegal I helped build a team of interactive developers while creating processes and wokflows.}
\\ \\ \\
\employer
	{TM}
	{http://tm.com/}
	{August 2006 --- January 2008}
	{Interactive Developer}
	{Provide a wide array of services to many notable clients; from web application development to email campaigns.}

\section{Talks and Presentations}

\begin{spacing}{1.25}
\href{https://speakerdeck.com/jakefolio/ruby-dot-new}{``Ruby.new"} presented at \href{http://openwest.org}{OpenWest 2013}
\\
\href{https://speakerdeck.com/jakefolio/building-a-css-foundation}{``Building a CSS Foundation"} presented at \href{http://html5tx.com}{HTML5.tx 2013}
\\
\href{https://speakerdeck.com/jakefolio/javascript-apis-in-the-html5-umbrella}{``Javascript APIs in the HTML5 Umbrella"} presented at \href{http://dallasphp.com}{DallasPHP 2013}
\\
\href{http://speakerdeck.com/u/jakefolio/p/iterators-in-php}{``Iterators in PHP"} presented at \href{http://confoo.ca}{Confoo 2012}
\\
\href{http://speakerdeck.com/u/jakefolio/p/building-more-with-less-css}{``Building more with LESS"} presented at \href{http://confoo.ca/}{Confoo 2012}
\\
\href{http://speakerdeck.com/u/jakefolio/p/css-selectors-the-next-generation}{``CSS Selectors: The Next Generation"} presented at \href{http://html5tx.com}{HTML5.tx}
\\
\href{http://speakerdeck.com/u/jakefolio/p/unsung-heroes-of-php}{``Unsung Heroes of PHP"} presented at \href{http://lonestarphp.com.com/}{Lone Star PHP 2011}
\\
\href{http://www.phparch.com/magazine/2011-2/october/}{``HTML5 Now (Article)"} published by \href{http://phparch.com/}{PHP Architecture}
\\
\end{spacing}

\section{Portfolio}

\begin{spacing}{1.25}
\href{http://lonestarphp.com/}{``Lone Star PHP Conference"}
\\
\href{http://www.bell525supermedium.net/}{``Bell Relentless"}
\\
\href{http://pedia-lax.com/}{``Pedialax"}
\\
\href{http://www.getlegal.com/}{``Get Legal"}
\\
\href{http://myavidgolfer.com/}{``Avid Golfer"}
\end{spacing}

\section{Education}

\stdtable{
School              & Midwestern State University \hfill Class of 2006\\
Degree              & B.A., Management Information Systems\\
}

\section{Awards/Certifications}

Zend Certified Engineer, (PHP 5.3)

\end{document}
